### 2021-05-23 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Final revision chpt 5 until compiler

How the assertions are associated with the respective entrypoint of the parent contract, may depend on the smart contract language. In the case of Solidity, a tag that mirrors the function name is enough to link assertion and entrypoint. In Michelson contracts, on the other hand, entrypoints can be anonymous. Therefore, the assertions are linked to the entrypoints through the tags, the parameter type or both. \secref{sec:typecheck} describes in more detail how the linking is implemented in the Tezos backend.

@@

After successfully parsing all assertions, the parser returns a list of their corresponding ASTs. \lstref{lst:ast_type} shows the toplevel definition of the AST type. It is composed of an entrypoint specification, consisting of an optional tag and the parameter pattern, and an assertion body. The parameter pattern and assertion body are subtrees representing their composition, or the nested assertion code respectively.
\begin{lstlisting}[label=lst:ast_type, language=, numbers=none, caption=Toplevel AST type definition in OCaml]
type ast =
  {entrypoint : string option * pattern; body : assertion}
\end{lstlisting}

>>>>

How the assertions are associated with the respective entrypoint of the parent contract, may depend on the smart contract language. In the case of Solidity, a tag that mirrors the function name is enough to link assertion and entrypoint. In Michelson contracts, on the other hand, entrypoints can be anonymous. Therefore, the assertions are linked to the entrypoints through the tags, the parameter type or both. How the linking is implemented in the Tezos backend is described in more detail in \secref{sec:typecheck}.

@@

After successfully parsing all assertions, the parser returns a list of their corresponding ASTs. \lstref{lst:ast_type} shows the toplevel definition of the AST type in OCaml. It is composed of an entrypoint specification, consisting of an optional tag and the parameter pattern, and an assertion body. The parameter pattern and assertion body are subtrees representing their composition, or the nested assertion code respectively.
\begin{lstlisting}[label=lst:ast_type, language=, numbers=none, caption=Toplevel AST type definition in OCaml]
type ast =
  {entrypoint : string option * pattern; body : assertion}
\end{lstlisting}
